Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2019-02-13 paper/snakemajoranas.tex
write about nanowires

\comment{We show that zigzag geometry solves this problem by eliminating the long trajectories.}
We propose a new experimental setup (see Fig.~\ref{fig:setup}(b)) for the creation of Majoranas that eliminating long trajectories and therefore prevents the appearance of a soft gap, while while also increasing the topological gap by several orders of magnitude, depending on the parameters.
The setup consists of a zigzag or snake-like geometry for the semiconductor where long trajectories are not possible due to the geometry.

@@

\comment{We consider a two-dimensional system with zigzag and BdG Hamiltonian.}
We consider a Josephson junction (Fig.~\ref{fig:setup}) consisting of a two-dimensional strip of semiconductor, with superconductors on both sides.
We modulate the shape of the normal region, which can be either saw-toothed zigzag as depicted [Fig.~\ref{fig:setup}(b)], or a more smooth sinusoidal-like shape.
Similar to the conventional straight system \cite{pientka2017topological}, a magnetic field $B_x$ perpendicular to the junction is applied.
We model the system with a Bogoliubov-de Gennes Hamiltonian (BdG) Eq.~\eqref{eq:hamiltonian}; the normal part has a linear Rashba spin-orbit coupling term characterized by $\alpha$ and a Zeeman field with $E_z=\frac{1}{2} \mu_B g B_x$.
The superconductor has a superconducting coupling term $\Delta$ with the pair of superconductors at an opposite superconducting phase $\exp{\pm i \phi/2}$.
Both the normal part and the superconducters have a kinetic term and chemical potential $\mu$.
The complete Hamiltonian has the form
\begin{equation}
\begin{split}
    H = & \left[\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu\right] \tau_z \\
        & + E_\text{z}(x,y) \sigma_x \\
        & + \alpha(x,y) \left( \ky \sigma_x - \kx \sigma_y \right) \tau_z
          + \Delta(x,y) \tau_y.
\end{split}
\label{eq:hamiltonian}
\end{equation}
It acts on the spinor wave function $\Psi={\left(\psi_{e\uparrow},\psi_{e\downarrow},\psi_{\textrm{h}\downarrow},-\psi_{\textrm{h}\uparrow}\right)}^{T}$, where $\psi_e$, $\psi_\textrm{h}$ are its electron and hole components, and $\psi_\uparrow$, $\psi_\downarrow$ are the spin-up and spin-down components.
The Pauli matrices $\sigma_{i}$ act on the spin degree of freedom and $\tau_{i}$ act on the electron-hole degree of freedom.
For the zigzag geometry, we first consider a sawtooth-like pattern where $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction.
The spatial dependence of $\Delta$, $E_z$, and $\alpha$ is explained in text above.
Later in this manuscript, we show that the exact details of the shape are unimportant and consider different zigzag geometries also parametrized by $z_x, \; z_y, \; W$.

>>>>

\comment{We show that zigzag geometry solves this problem by eliminating the long trajectories.}
We propose a new experimental setup (see Fig.~\ref{fig:setup}(b)) for the creation of Majoranas that eliminating long trajectories and therefore prevents the appearance of a soft gap, while while also increasing the topological gap by several orders of magnitude, depending on the parameters.
The setup consists of a zigzag or snake-like geometry for the semiconductor where long trajectories are not possible due to the geometry.
In this paper we will focus on two-dimensional (2D) Josephson junctions, however, a zigzag geometry will also work for nanowires.\footnote{We confirmed this numerically, although it is not included in this paper.}

@@

\comment{We consider a two-dimensional system with zigzag and BdG Hamiltonian.}
We consider a Josephson junction (Fig.~\ref{fig:setup}) consisting of a 2D strip of semiconductor, with superconductors on both sides.
We modulate the shape of the normal region, which can be either saw-toothed zigzag as depicted [Fig.~\ref{fig:setup}(b)], or a more smooth sinusoidal-like shape.
Similar to the conventional straight system \cite{pientka2017topological}, a magnetic field $B_x$ perpendicular to the junction is applied.
We model the system with a Bogoliubov-de Gennes Hamiltonian (BdG) Eq.~\eqref{eq:hamiltonian}; the normal part has a linear Rashba spin-orbit coupling term characterized by $\alpha$ and a Zeeman field with $E_z=\frac{1}{2} \mu_B g B_x$.
The superconductor has a superconducting coupling term $\Delta$ with the pair of superconductors at an opposite superconducting phase $\exp{\pm i \phi/2}$.
Both the normal part and the superconducters have a kinetic term and chemical potential $\mu$.
The complete Hamiltonian has the form
\begin{equation}
\begin{split}
    H = & \left[\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu\right] \tau_z \\
        & + E_\text{z}(x,y) \sigma_x \\
        & + \alpha(x,y) \left( \ky \sigma_x - \kx \sigma_y \right) \tau_z
          + \Delta(x,y) \tau_y.
\end{split}
\label{eq:hamiltonian}
\end{equation}
It acts on the spinor wave function $\Psi={\left(\psi_{e\uparrow},\psi_{e\downarrow},\psi_{\textrm{h}\downarrow},-\psi_{\textrm{h}\uparrow}\right)}^{T}$, where $\psi_e$, $\psi_\textrm{h}$ are its electron and hole components, and $\psi_\uparrow$, $\psi_\downarrow$ are the spin-up and spin-down components.
The Pauli matrices $\sigma_{i}$ act on the spin degree of freedom and $\tau_{i}$ act on the electron-hole degree of freedom.
For the zigzag geometry, we first consider a sawtooth-like pattern where $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction.
The spatial dependence of $\Delta$, $E_z$, and $\alpha$ is explained in text above.
Later in this manuscript, we show that the exact details of the shape are unimportant and consider different zigzag geometries also parametrized by $z_x, \; z_y, \; W$.
